Solar-Electric and Gas Powered, Long-Endurance UAV Sizing via Geometric Programming

### 2017-05-21 docs/thesis/chap_results.tex
modify gas to include sp bool; print tail boom table for gas; create appendix and tbflex section in thesis

@@

@@

>>>>

\subsection{Representing Structural Weight as Fraction of Total}

@@

\subsection{Lift to Drag Ratio Shift Due to Wind Speed Constraint}

@@

\subsection{Tail Boom Flexibility}

By changing using higher fidelity physical models, more accurate results of the sizing analysis can be achieved.  
For example, sizing the horizontal tail using a volume coefficient does not account for the fexibility of the tail boom. 
A flexible tail boom will cause a slight delay in the responsiveness to pitch control inputs, effectively lowering the control authority of the horizontal tail. 
However, using a minimum static margin $\text{SM}_{\text{min}} = 0.35$ and minimum desirable c.g. travel range,

\begin{equation}
    \label{e:deltacg}
    \Delta x_{cg} = (x_{cg})_{\text{aft}} - (x_{cg})_{\text{fwd}} = 0.2,
\end{equation}

a single constraint, whose derivation is explained in Appendix~\ref{app:tbflex}, minimizes the horizontal tail volume coefficient $V_{\text{w}}$, while meeting the minimum static margin and minimum c.g. travel range,

\begin{equation}
    \label{e:smcorr}
    \text{SM}_{\text{min}} + \frac{\Delta x_{cg}}{c} - \frac{C_{M_{	ext{w}}}}{C_{L_{\text{max}}}} \leq V_{\text{w}} \mathcal{F}_{NE}^{-1} \frac{m_{\text{h}}}{m_{\text{w}}} \left( 1 - \frac{d\epsilon}{d\alpha}\right) + V_{\text{w}} \frac{-(C_{L_{\text{h}}})_{\text{min}}}{C_{L_{\text{max}}}} \\
\end{equation}

Because this equation is not GP-compatible a signomial program is used to solve the optimization model for both the solar-electric and gas powered models.\cite{sp}
The flexibility factor,

\begin{equation}
     \mathcal{F} = 1 + m_{\text{h}} \frac{qS_{\text{h}}l_{\text{h}}^2}{EI_0}(1-\frac{1}{2}k) 
\end{equation}

is a measure of how the pitch control authority is degraded by the flexibility of the tail boom. 
Thus, it is expected that the horizontal tail volume coefficient will increase from an increased horizontal tail surface area and tail boom length. 
Tables~\ref{t:tbftable} and~\ref{t:tbfgtable} confirm the increased size of the horizontal tail and tail boom when the tail boom flexibility model is activiated.

\input{../tbftable.generated.tex}
\input{../tbfgtable.generated.tex}
